Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-05-07 gullydiss.tex
I think this is the final version to submit to the Graduate School

This work would not have been possible without the mentorship of my collaborators Katelyn Allers and Alycia Weinberger, for which I am deeply indebted.  I acknowledge the mentorship and patience of my former student colleagues Dr. Jasmina Marsh and Dr. Casey Deen.  I am grateful for the efforts of my junior colleagues Jared Rand, Amanda Turbyfill, and Carleen Boyer for their contributions to the Silicon Diffractive Optics Group.  Engineers Weisong Wang and Cindy Brooks contributed substantially to the Si diffractive optics fabrication.  I am indebted to my NASA GRSP mentor Daniel Wilson, with whom it was a pleasure to work.  I am thankful for the supervision of Richard Muller and Victor White at the Microdevices Laboratory.

@@

I was lucky to be part of such a talented and creative group of incoming graduate students- Chris, John, Chalence, JJ, Julie, Manuel, Erik, Paul, and Manos.  I look forward to following their promising careers, and crossing paths indefinitely.  Joi Ito and the Minor Mishap Marching Band enhanced my creativity.  Thank you to my supportive family members Diana, Tony, Erika, and Vanessa who gave me mettle.  Thank you to Carol Contillo for bringing Chelsey into the world, to Alese for introducing us, and to Chelsey for being exceptionally supportive.  Thanks to all my friends.  I acknowledge the kindness of the Wolchover family, who have always been out standing in their field.

@@

Using deep optical, near-infrared, and mid-infrared photometry, I search an off-core region towards the nearby $\sim1 Myr$ \emph{Ophiuchus} star forming cluster for candidate young stars and brown dwarfs.  Multi-object $I-$band spectroscopy of 419 candidates reveals 12 new members.  Ten of these have no evidence for mid-IR excess emission from 3.6 to 8.0 $\mu$m.  The disk fraction for spectral types M4 and later towards this region of \emph{Ophiuchus} is 5/15.  Two of the disk sources have edge-on disks, pointing to a high edge-on disk fraction.  I discuss possible sources of contamination in the survey.

>>>>

This work would not have been possible without the mentorship of my collaborators Katelyn Allers and Alycia Weinberger, for which I am deeply indebted.  I acknowledge the mentorship and patience of my former student colleagues Dr. Jasmina Marsh and Dr. Casey Deen.  I am grateful for the efforts of my junior colleagues Jared Rand, Amanda Turbyfill, and Carleen Boyer for their contributions to the Silicon Diffractive Optics Group.  Engineers Weisong Wang and Cindy Brooks contributed substantially to the Si diffractive optics fabrication.  I am indebted to my NASA GRSP mentor Daniel Wilson, with whom it was a pleasure to work.  I am thankful for the supervision of Richard Muller and Victor White at the Microdevices Laboratory.  Sungho Lee, Hyeonju Jeong, Taylor Chonis, Mike Pavel, Michelle Grigas, Neal Evans, John Lacy, and Adam Kraus, Rachel Walker, and Gordon Orris made this work possible.

@@

I was lucky to be part of such a talented and creative group of incoming graduate students- Chris, John, Chalence, JJ, Julie, Manuel, Erik, Paul, and Manos.  I look forward to following their promising careers, and crossing paths indefinitely.  Joi Ito and Datri Bean enhanced my creativity.  Thank you to my supportive family members Diana, Tony, Erika, and Vanessa who gave me mettle.  Thank you to Carol for bringing Chelsey into the world, to Alese for introducing us, and to Chelsey for being exceptionally supportive.  Thanks to Mr. Emerson who got me started in astronomy.  Thanks to all my friends.  I acknowledge the kindness of the Wolchover family, who have always been out standing in their field.

@@

Using deep optical, near-infrared, and mid-infrared photometry, I search an off-core region towards the nearby $\sim1$ Myr \emph{Ophiuchus} star forming cluster for candidate young stars and brown dwarfs.  Multi-object $I-$band spectroscopy of 419 candidates reveals 12 new members.  Ten of these have no evidence for mid-IR excess emission from 3.6 to 8.0 $\mu$m.  The disk fraction for spectral types M4 and later towards this region of \emph{Ophiuchus} is 5/15.  Two of the disk sources have edge-on disks, pointing to a high edge-on disk fraction.  I discuss possible sources of contamination in the survey.
